Noncoherent least squares estimators of carrier phase and amplitude

### 2012-10-23 other/confnoncoherent/paper.tex
modifed conference paper to fit with ICASSP template

%\documentclass[a4paper,10pt]{article}
%\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
\documentclass[conference]{IEEEtran}

\usepackage{mathbf-abbrevs}
\input{defs}

@@

\usepackage[square,comma,numbers,sort&compress]{natbib}

@@

%opening
\title{Noncoherent least squares estimators of carrier phase and amplitude}
\author{Robby McKilliam$^{1}$, Andr\'{e} Pollok$^{1}$, Bill Cowley$^{1}$, Vaughan Clarkson$^{2}$ and Barry Quinn$^{3}$ \vspace{0.2cm} \\
\small $^{1}$Institute for Telecommunications Research, University of South Australia, SA, \textsc{Australia} \vspace{0.1cm} \\
\small $^{2}$School of Information Technology \& Electrical Engineering, The University of Queensland, QLD 4067, \textsc{Australia} \vspace{0.1cm} \\
\small $^{3}$Department of Statistics, Macquarie University, Sydney, \textsc{Australia} 
\thanks{Supported under the Australian Government’s Australian Space Research Program.}
}

\IEEEoverridecommandlockouts
\begin{document}

@@

\begin{abstract}
We consider least squares estimators of carrier phase and amplitude from a noisy communications signal.  We focus on signaling constellations that have symbols evenly distributed on the complex unit circle, i.e., $M$-ary phase shift keying.  We show, under reasonably mild conditions on the distribution of the noise, that the least squares estimator of carrier phase is strongly consistent and asymptotically normally distributed.  However, the amplitude estimator is not consistent, it converges to a positive real number that is a function of the true carrier amplitude, the noise distribution, and the size of the constellation.  The results of Monte Carlo simulations are provided and these corroborate the theoretical results.
\end{abstract}
\begin{IEEEkeywords}
Noncoherent detection, phase shift keying, asymptotic statistics
\end{IEEEkeywords}

@@

We will have particular use of complex random variables of the form $1 + X$ where $X$ is circularly symmetric.  Let $R \geq 0$ and $\Phi \in [0,2\pi)$ be real random variables satisfying, 
\[
R e^{j\Phi} = 1 + X.
\]
The joint distribution of $R$ and $\Phi$ can be shown to be
\[
f(r,\phi) = \frac{r f_Z(\sqrt{r^2 - 2r\cos\phi + 1})}{2\pi\sqrt{r^2 - 2r\cos\phi + 1}}.
\]
% The mean of $R e^{j\Phi}$ is equal to one because the mean of $X$ is zero.  So,
% \[
% \expect \Re(R e^{j\Phi}) = \expect R \cos(\Phi) = 1,
% \]
% where $\Re(\cdot)$ denotes the real part, and
% \[
% \expect \Im(R e^{j\Phi}) = \expect R \sin(\Phi) = 0,
% \]
% where $\Im(\cdot)$ denotes the imaginary part.  %The next lemma will be useful for the analysis of the least squares estimator.

@@

\section{Conclusion}

>>>>

%\documentclass[a4paper,10pt]{article}
%\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
%\documentclass[conference]{IEEEtran}

\documentclass{article}

\usepackage{spconf}

\usepackage{mathbf-abbrevs}

\input{defs}

@@

%NOTE: If you use the natbib package, you should use natbibspacing.sty instead, and be sure to load it after natbib:
\usepackage[square,comma,numbers,sort&compress]{natbib}
\usepackage{natbibspacing}
\setlength{\bibspacing}{0cm}

@@

% %opening
% \title{Noncoherent least squares estimators of carrier phase and amplitude}
% \author{Robby McKilliam$^{1}$, Andr\'{e} Pollok$^{1}$, Bill Cowley$^{1}$, Vaughan Clarkson$^{2}$ and Barry Quinn$^{3}$ \vspace{0.2cm} \\
% \small $^{1}$Institute for Telecommunications Research, University of South Australia, SA, \textsc{Australia} \vspace{0.1cm} \\
% \small $^{2}$School of Information Technology \& Electrical Engineering, The University of Queensland, QLD 4067, \textsc{Australia} \vspace{0.1cm} \\
% \small $^{3}$Department of Statistics, Macquarie University, Sydney, \textsc{Australia} 
% \thanks{Supported under the Australian Government’s Australian Space Research Program.}
% }

 \title{Noncoherent least squares estimators of carrier phase and amplitude}
\name{Robby McKilliam$^{1}$, Andr\'{e} Pollok$^{1}$, Bill Cowley$^{1}$, Vaughan Clarkson$^{2}$ and Barry Quinn$^{3}$ \thanks{Supported under the Australian Government’s Australian Space Research Program.}}
\address{ \small $^{1}$Institute for Telecommunications Research, University of South Australia, SA, \textsc{Australia} \vspace{0.05cm} \\
\small $^{2}$School of Information Technology \& Electrical Engineering, The University of Queensland, QLD 4067, \textsc{Australia} \vspace{0.05cm} \\
\small $^{3}$Department of Statistics, Macquarie University, Sydney, \textsc{Australia} 
}

%\IEEEoverridecommandlockouts
\begin{document}

@@

\begin{abstract}
We consider least squares estimators of carrier phase and amplitude from a noisy communications signal.  We focus on signaling constellations that have symbols evenly distributed on the complex unit circle, i.e., $M$-ary phase shift keying.  We show, under reasonably mild conditions on the distribution of the noise, that the least squares estimator of carrier phase is strongly consistent and asymptotically normally distributed.  However, the amplitude estimator is not consistent, it converges to a positive real number that is a function of the true carrier amplitude, the noise distribution, and the size of the constellation.  The results of Monte Carlo simulations are provided and these corroborate the theoretical results.
\end{abstract}
\begin{keywords}
Noncoherent detection, phase shift keying, asymptotic statistics
\end{keywords}

@@

We will have particular use of complex random variables of the form $1 + X$ where $X$ is circularly symmetric.  Let $R \geq 0$ and $\Phi \in [0,2\pi)$ be real random variables satisfying, 
\[
R e^{j\Phi} = 1 + X.
\]
The joint distribution of $R$ and $\Phi$ can be shown to be
\[
f(r,\phi) = \frac{r f_Z(\sqrt{r^2 - 2r\cos\phi + 1})}{2\pi\sqrt{r^2 - 2r\cos\phi + 1}}.
\]

% The mean of $R e^{j\Phi}$ is equal to one because the mean of $X$ is zero.  So,
% \[
% \expect \Re(R e^{j\Phi}) = \expect R \cos(\Phi) = 1,
% \]
% where $\Re(\cdot)$ denotes the real part, and
% \[
% \expect \Im(R e^{j\Phi}) = \expect R \sin(\Phi) = 0,
% \]
% where $\Im(\cdot)$ denotes the imaginary part.  %The next lemma will be useful for the analysis of the least squares estimator.

@@

\section{RELATION TO PRIOR WORK}
